\documentclass[conference,compsoc]{IEEEtran}

\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

\usepackage{listings}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{booktabs}
\floatname{algorithm}{algorithm} 
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{array}
\usepackage{url}
\hyphenation{op-tical net-works semi-conduc-tor}
\begin{document}

\title{Gomoku Project}
\author{\IEEEauthorblockN{Wang Zhiyuan  11610634}
\IEEEauthorblockA{CSE\\
Computer Science and Technology\\
11610634@mail.sustc.edu.cn}}
\maketitle
\IEEEpeerreviewmaketitle



\section{Preliminaries}

\subsection{Software}
For this project, I write it by Python. The package I have used is use $numpy$ and $copy$
\subsection{Algorithm}
For this Project, I use the method of heurlstlc search. The primary part of this Algorithm is the design of the 
evaluation function.  

And to optimize the Algorithm, I use the Min-Max Analysis to design a game tree, and use Alpha-Beta purning to simplify the process of search. 
But limited by the time. The depth of the tree should less then 8.

\section{Methodology}
\subsection{Representation}
In my code, according to the example given by the teacher, I design six method:  
\begin{itemize}
  \item $count()$
  \item $calcute\_value()$
  \item $get\_pos\_value()$
  \item $get\_pos\_list()$
  \item $tree()$
  \item $go()$
\end{itemize}
For these methods:
\begin{itemize}
  \item The $go()$ is the method that test program will call.
  \item The $count()$, $calcute\_value()$ and $get\_pos\_value()$ can calucute the value of each coordinate in the chessboard which is null now.
  \item The $get\_pos\_list()$ and $tree()$ will build a game tree.
\end{itemize}

\subsection{Architecture}
\begin{itemize}
  \item $go()$
  \begin{itemize}
    \item $count()$
    \item $calucute\_value()$
    \item $get\_pos\_value()$
    \item $calcute\_pos\_list()$
    \item $tree()$
    \begin{itemize}
      \item $count()$
      \item $calucute\_pos\_value()$
      \item $get\_pos\_value()$ 
      \item $calcute\_pos\_list()$
    \end{itemize}
  \end{itemize}
\end{itemize}

\subsection{Detail of Algorithm}
  Firstly, I need to design a evaluation function to get the value of all the coordinate with null color.
  I calculate the value of one location by combinate the conditions of 8 directions of this coordinate:
  \begin{itemize}
    \item Count how many chess with he same color as yours in one direction
    \item Count how many chess with the same color as yours if there is one null chess in one direction
    \item In the end of this direction is null chess or the versus color chess.
  \end{itemize}
  \begin{algorithm}
    \caption {Count}
    \begin{algorithmic}[1]
      \Function {count}{$self, chessboard, a, b, j, k, COLOR$}
      \State $  i\gets 0  $
      \State $  m\gets 0  $
      \State $  flag\gets 0  $
          \While{$ (-1 < a + j < 15  $ $\textbf{and}$ $  -1 < b + k < 15  $ $\textbf{and}$ $  chessboard[a + j, b + k] != -COLOR): $}
              \If{$ chessboard[a + j, b + k] == COLOR: $}
                  \If{$ flag == 0: $}
                  \State $  i\gets i + 1  $
                  \Else:
                  \State $  m\gets m + 1  $
              \State $  a\gets a + j  $
              \State $  b\gets b + k  $
                  \EndIf
              \Else:
                  \If{$ -1 < a + 2 * j < 15  $ $\textbf{and}$ $  -1 < b + 2 * k < 15: $}
                      \If{$ chessboard[a + (2 * j), b + (2 * k)] == COLOR  $ $\textbf{and}$ $  flag == 0: $}
                      \State $  m\gets i  $
                      \State $  flag\gets 1  $
                      \State $  a\gets a + j  $
                      \State $  b\gets b + k  $
                      \Else:
                          break
                      \EndIf
                  \Else:
                      break
                  \EndIf
              \EndIf
          \EndWhile

          \If{$ (-1 < a + j < 15  $ $\textbf{and}$ $  -1 < b + k < 15): $}
              \If{$ chessboard[a + j, b + k] == COLOR\_NONE: $}
              \State $  i\gets i * 2  $
              \State $  m\gets m * 2  $
              \Else:
              \State $  m\gets m * 2 - 1  $
              \State $  i\gets i * 2 - 1  $
              \EndIf
          \Else:
          \State $  i\gets i * 2 - 1  $
          \State $  m\gets m * 2 - 1  $
          \EndIf
          return [i, m]
      \EndFunction
    \end{algorithmic}
  \end{algorithm}
  
  After get the conditions of all the 8 directions of the null chess coordinates.
  I can combinate two direction in one line and get the result in this line.
  \begin{itemize}
    \item In the \textbf{algorithm 1}. The list returned have two integer:
          \begin{itemize} 
            \item The first number show the status in this direction that without any null chess.
            \item The second number show the status in this direction that with one and only one null chess.
            \item For each number: If the number of the chess with self.color is $n$, then the value will be $2\times n$ while there is null chess at the end, or the value will be $2\times n -1$
          \end{itemize}
    \item According to the sum of the value of the two directions in one line, I can get the chess shape in this line. You can get the detail in the \textbf{algorithm 2} and the value append corresponding to the chess shape is shown on \textbf{TABLE 1.}.
    \item Then I will statistics the shapes on the 4 lines and give the weight value.
  \end{itemize}

  \begin{table}[!htbp]
    \centering
    \caption{The Table of The Chess Shape}\label{tab:aStrangeTable}
    \begin{tabular}{|c|c|}
      \hline
      \textbf{The SUM} & \textbf{Chess Shape}\\
      \hline
      1 & Five chesses\\
      \hline
      2 & Four chesses without different color chess\\
      \hline
      3 & Four chesses with a different color chess on the end\\
      \hline
      4 & Three chesses without different color chess\\
      \hline
      5 & Three chesses with a different color chess on the end\\
      \hline
      6 & Two chesses without different color chess\\
      \hline
      7 & Two chesses with a different color chess on the end\\
      \hline
      8 & One chess without different color chess\\
      \hline
      9 & One chess with a different color chess on the end\\
      \hline
      10 & Some chesses with two different color chesses\\
      \hline
    \end{tabular}
  \end{table}
  \begin{algorithm}
    \caption{Calculate\_value}
    \begin{algorithmic}[1]
      \Function{Value\_Of\_Line}{$i1, i2, m1, m2$}
      \State $ flag = i1 + i2 $
        \If {$ flag > 6 $}
        \State $ y.append(1) $
            \ElsIf {$ flag == 6 $}
                \If {$ (i1 * i2 < 0 \textbf{or} i1 == i2 \textbf{or} (i1 == 5 \textbf{or} i2 == 5)) $}
            \State $ y.append(1)   $
            \Else:
            \State $ y.append(2)   $
            \EndIf
        \ElsIf {$ flag == 5 $}
            \State $ y.append(3)   $
        \ElsIf {$ flag == 4 $}
            \If {$ (i1 * i2 < 0) $}
            \State $ y.append(10)   $
            \Else:
            \State $ y.append(4)   $
            \EndIf
        \ElsIf {$ flag == 3 $}
        \State $ y.append(5)   $
        \ElsIf {$ flag == 2 $}
            \If {$ (i1 == i2 \textbf{or} i1 * i2 < 0) $}
            \State $ y.append(10)   $
            \Else:
            \State $ y.append(6)   $
            \EndIf
        \ElsIf {$ flag == 1 $}
        \State $ y.append(7)   $
        \ElsIf {$ flag == 0 $}
            \If {$ (i1 * i2) == 0 $}
            \State $ y.append(8)   $
            \Else:
            \State $ y.append(10)   $
            \EndIf
        \ElsIf {$ flag == -1 $}
        \State $ y.append(9)   $
        \EndIf %\EndIf \EndIf \EndIf \EndIf \EndIf \EndIf \EndIf \EndIf

        \If {$ (m1 > 5 \textbf{or} m2 > 5) $}
        \State $ y.append(3) $
        \ElsIf {$ (m1>3 \textbf{and} x[i+4][0]>1)\textbf{or} (m2>3 \textbf{and} i1>1) $}
        \State $ y.append(3) $
        \ElsIf {$ (i1>1 \textbf{and} m2>1) \textbf{or} (m1>1 \textbf{and} x[i+4][0]>1) $}
        \State $ y.append(4) $
        \ElsIf {$ (i1>=0 \textbf{and} m2>3) \textbf{or} (m1>3 \textbf{and} x[i+4][0]>=0) $}
        \State $ y.append(4) $
        \EndIf %\EndIf \EndIf \EndIf
      \EndFunction
    \end{algorithmic}
  \end{algorithm}

  Then, I will build the game tree with the evaluation fucntion I design above:
  \begin{itemize}
    \item Use the evaluation function get the list include the points with thee biggest weight value.
    \item Use each point in the list as the max layer and build the game tree.
    \item Add the Alpha-Beta value attribute and set the threshold value of Beta-Alpha to purning.
    \item The \text{algorithm 3.} is the algorithm to build the tree. In this algorithm, I do purning when the points have Beta value is not bigger than its Alpha value.
  \end{itemize}
  \begin{algorithm}
    \caption{game\_tree}
    \begin{algorithmic}[1]
      \Function{tree}{$chessboard,value,pos\_list,time$}
      \For{$ pos \in pos\_list $}
      \If {$ time < 8 $}
      \State $ chessboard[pos[0],pos[1]] \gets alpha\_beta $
      \State $ pos\_list\_temp \gets$\Call{get\_pos\_list}{$$ chessboard, -alpha\_beta $$}
      \State $ value\_temp\gets$\Call{tree}{$$ chessboard,-alpha\_beta,value,pos\_list\_temp,time+1 $$}
      \State $ chessboard[pos[0], pos[1]]\gets 0 $
          \If {$ alpha\_beta == color $}
              \If {$ value\_temp[1] > value[0] $}
              \State $ value[0]\gets value\_temp[1]$
              \EndIf
          \Else
              \If {$ value\_temp[0] < value[1] $}
              \State $ value[1]\gets value\_temp[0]$
              \EndIf
              \EndIf    
          \If {$ value[0]+2 >= value[1] $}
          \State $ break $
          \EndIf    
      \Else
      \State $ chessboard[pos[0], pos[1]]\gets alpha\_beta $
      \State $ value\_temp \gets$\Call{calcute\_value}{$$ chessboard, pos[0], pos[1], alpha\_beta $$}
      \State $ interger\gets interger + 1 $
      \State $ chessboard[pos[0], pos[1]]\gets 0 $
      \State $ value[0]\gets value_temp $
      \EndIf
    \EndFor
        \EndFunction
      \end{algorithmic}
  \end{algorithm}

\section{Empirical Verification}
\subsection{Design}
For the verification part. I use a flight platform and design three ways to test it:
\begin{itemize}
  \item Flight with it by myself and observe if have any problem
  \item Set some initial sitiuation that check if the algorithm work as I design
  \item Use the AI VS Platform.In on 10.20.96.148 to test the code.
\end{itemize}
\subsection{Performance}
For the Time Performance:
\begin{itemize}
  \item If I just use the evalution function to get the list of the points with the highest weight value and random to get one point as the result I submit. The speed of the AI will be very fast even ignore it.
  \item If I  build a game tree and use Alpha-Beta value method to purning. If I limit the depth of the tree less then 8 and the size of the list less then 20, each step can be finished in 5 second.
\end{itemize}

\subsection{Result}
For the capacity of the program, I have use this program play with a Gomoku game of Tecent, this program can win in most of time.
\subsection{Analysis}
For this project, I think the most important part is the design of the evaluation, for that the structure of the game tree is same in most of time, and limited by the time we can't search deeply enough. 
So if the evaluation consider many enough shapes of the chess, and assign suitabe weight value, it can be seem that the depth of the tree has been boost a lot with a little time cost.




\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,mylib}
\cite{rivest1987game}
\cite{knuth1975analysis}

\end{document}


